### 2014-03-01 paper/real.tex
wip

\subsection{C}
\label{sec:real:c}

>>>>

\subsection{C}
\label{sec:real:c}
%
Within the confine of a process, C program can execute arbitrary
(machine) code, access arbitrary memory, and perform arbitrary
syscalls.
%
C code is only confined to degree imposed by by underlying OS and
hardware.
%
Hence implementing an IFC system according to the specification
language of Section~\ref{sec:retrofit} must address these concerns.

Nevertheless, we believe that an implementation that adheres to our
specification under the |roundrobinf| scheduler can be achieved
without too much effort.
%
(Our proposed approach, below, is very similar to a simpler version of
Wedge~\tocite{}, with an IFC policy.)
%
Specifically, we propose a system, HIPStar, that uses hardware
protection mechanisms to isolate untrusted code according to an IFC
policy (implemented by a small runtime) in user-space, with
Dune~\tocite{}.
%
Using pages tables, our (trusted) IFC runtime ensures that each task,
implemented as a lightweight process can only access the memory it
allocates--tasks do not have access to any shared memory.
%
In addition, we use ring protection to intercept syscalls performed by
a task and only permit those corresponding to our IFC language (e.g.,
|getLabel|, |send|).
%

Although other sandboxing mechanisms can be used in place of Dune, we
believe Dune's hardware protection mechanism allow us to provide a 
concrete implementation that is simpler to reason about.
%
To this end, the combined language of Section~\ref{sec:retrofict}
corresponds to C with the additional IFC syscalls.
%
Creating a new task with the |fork| syscall ensures that no memory is
shared, by defining |kappa(tS) = tS0|, where |tS0| is the set of pages
we copy to bootstrap the lightweight process.
%
Similarly, sending a message with |send| results in a copying the
pages to our (trusted) runtime, and, then the (untrusted) receiver.
%
Of course, a more efficient message-passing approach, such as that of
Singularity~\tocite{}, which simply passes a pointer to data the
receiver at the cost of revoking the sender's access to the pages is
also possible.
